Report on Late Winter2013 Production: Image Differencing

### 2013-03-22 W13report.tex
Fixing latex refs and moving figures

The numbers of false detections in each best case are given in
Table~\ref{tab-bestfp10a}.  We undertook a manual inspection of all
difference images to associate the DiaSources with Sources in the
images, and also a 3'' association with the input source catalog.
These associations are listed in the N$_{Match}$ column of
Table~\ref{tab-bestfp10}, with the unmatched false positives in the
N$_{Orphan}$ column.  The former are likely to come from systematics
in the subtractions of stars, while the latter would be due to
fluctuations in the background.  We note 2 effects that will impact
N$_{Match}$.  The first is that, with a 3'' matching radius, 4\% of
random fluctuations will by--chance associate with a Source.  Assuming
that N$_{Orphan}$ represents 96\% of the background fluctuation
population, we estimate the number of fluctuations from that same
population that would have associated with Sources as N$_{Random}$.
Finally, we count all matches that occur within 100 pixels of the
image boundary, where we might expect the spatial extrapolation to
yield systematic residuals, as N$_{D<100}$.  To the extent that
(N$_{Random}$ + N$_{D<100}$) < N$_{Match}$, we have a small residual
set of systematic false detections in our imaging ensemble.  Aside
from the deconvolution run, this is at the level of 10 total false
detections over 9 sensors in 5 production runs, or 1 every 4--5
images.

@@

\subsection{Background Subtraction {\bf SIMON}}

@@

\clearpage
%\begin{table}
%\centering
%\begin{tabular}{clcc}
%\hline
%\multicolumn{4}{|c|}{Best Results: Production 8} \\
%\hline
%Visit    & Prefilter & False Detection Matches & False Detection Orphans \\
%\hline
%v6866601 & True      & 5                      & 29  \\
%         & False     & 10                     & 81  \\
%v6866602 & True      & 5                      & 30  \\
%         & False     & 9                      & 35  \\
%v6866603 & True      & 2                      & 9   \\
%         & False     & 1                      & 23  \\
%\end{tabular}
%\caption{Total number of {\tt DiaSources} detected at 5--sigma from
%  all 9 sensors in raft 2,2, for the configurations that yielded the
%  lowest number of false detections.  Matches are determined using a
%  3'' match radius with the input reference catalog.  Objects with the
%  {\tt EDGE} flag are ignored. \label{tab-bestfp8}}
%\end{table}

\begin{table}
\centering
\begin{tabular}{clcccccc}
\hline
\multicolumn{8}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & Total False Detections &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & Nneg / Npos \\
\hline
v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
         & False     & 143     &51         & 92 & 2     & 11  & 0.4 \\
v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.6 \\
         & False     & 53      &45         & 8  & 2     & 1   & 0.5 \\
v6866603 & True      & 23      &23         & 0  & 1     & 0   & 2.8 \\
         & False     & 36      &35         & 1  & 1     & 0   & 3.4 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false detections.  Matches are determined using a
  3'' match radius with the input reference catalog.  Objects with the
  {\tt EDGE} flag are ignored.  We list the number of background
  fluctuations that are expected to randomly associate with a Source
  N$_{Random}$, given the density of objects in the images and a 3''
  match radius, assuming that N$_{Orphan}$ represents 96\% of the
  total population of detections arriving from Gaussian fluctuations.
  We also list the number of false detections that are found within
  the outer 100 pixels of the image N$_{D<100}$.  The final column
  lists ratios of the number of negatively detected false detections
  to those with positive flux, a 5--sigma. \label{tab-bestfp10a}}
\end{table}

\begin{table}
\centering
\begin{tabular}{clccc}
\hline
\multicolumn{5}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & False Detections: Matches & False Detections: Orphans & Nneg / Npos \\
\hline
v6866601 & True      & 11                        & 59  & 1.8 \\ 
         & False     & 99                        & 44  & 2.9 \\
v6866602 & True      & 7                         & 35  & 2.2 \\
         & False     & 8                         & 45  & 0.7 \\
v6866603 & True      & 1                         & 22  & 2.8 \\
         & False     & 1                         & 35  & 3.0 \\
%v6866601 & True      & 11                        & 70  & 1.8 \\ SUBTRACT ME!
%         & False     & 99                        & 143 & 2.9 \\
%v6866602 & True      & 7                         & 42  & 2.2 \\
%         & False     & 8                         & 53  & 0.7 \\
%v6866603 & True      & 1                         & 23  & 2.8 \\
%         & False     & 1                         & 36  & 3.0 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false detections.  Matches are determined using a
  3'' match radius with the input reference catalog.  Objects with the
  {\tt EDGE} flag are ignored.  The final column lists ratios of the
  number of negatively detected false detections to those with
  positive flux. \label{tab-bestfp10b}}
\end{table}

%\begin{table}
%\centering
%\begin{tabular}{clccc}
%\hline
%\multicolumn{5}{|c|}{Best Configs: Production 8} \\
%\hline
%Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
%\hline
%v6866601 & True      & 3      & 6        & 5 \\
%         & False     & 3      & 2        & 4 \\
%v6866602 & True      & 3      & 6        & 5 \\
%         & False     & 3      & 5        & 5 \\
%v6866603 & True      & 3      & 6        & 4 \\
%         & False     & 3      & 6        & 4 \\
%\end{tabular}
%\caption{Configurations that led to the best results listed in
%  Table~\ref{tab-bestfp8}.  All post-production runs include
%  perturbations about these configurations. \label{tab-bestconfig8}}
%\end{table}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
\caption{``Heat--map'' detailing the total numbers of 5--sigma false
  positives as a function of two main degrees of freedom: the maximum
  order of basis Laguerre polynomials along the y--axis, and the
  spatial order of the Chebyshev expansion of the spatial model along
  the x--axis.  The {\it left} column shows these results for
  prefiltering, while the {\it right} column shows this for the
  post--filtered analysis.  The best results listed in
  Table~\ref{tab-bestfp}, with the associated configurations from
  Table~\ref{tab-bestconfig}, correspond to the minimum in each of the
  subpanels.  }
\label{fp_heatmap}
\end{figure}

>>>>

The numbers of false detections in each best case are given in
Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
difference images to associate the DiaSources with Sources in the
images, and also a 3'' association with the input source catalog.
These associations are listed in the N$_{Match}$ column of
Table~\ref{tab-bestfp10}, with the unmatched false positives in the
N$_{Orphan}$ column.  The former are likely to come from systematics
in the subtractions of stars, while the latter would be due to
fluctuations in the background.  We note 2 effects that will impact
N$_{Match}$.  The first is that, with a 3'' matching radius, 4\% of
random fluctuations will by--chance associate with a Source.  Assuming
that N$_{Orphan}$ represents 96\% of the background fluctuation
population, we estimate the number of fluctuations from that same
population that would have associated with Sources as N$_{Random}$.
Finally, we count all matches that occur within 100 pixels of the
image boundary, where we might expect the spatial extrapolation to
yield systematic residuals, as N$_{D<100}$.  To the extent that
(N$_{Random}$ + N$_{D<100}$) < N$_{Match}$, we have a small residual
set of systematic false detections in our imaging ensemble.  Aside
from the deconvolution run, this is at the level of 10 total false
detections over 9 sensors in 5 production runs, or 1 every 4--5
images.

@@

\subsection{Background Subtraction {\bf SIMON} \label{sec-bg}}

@@

\clearpage
\begin{table}
\centering
\begin{tabular}{clcccccc}
\hline
\multicolumn{8}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & Total False Detections &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & Nneg / Npos \\
\hline
v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
         & False     & 143     &51         & 92 & 2     & 11  & 0.4 \\
v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.6 \\
         & False     & 53      &45         & 8  & 2     & 1   & 0.5 \\
v6866603 & True      & 23      &23         & 0  & 1     & 0   & 2.8 \\
         & False     & 36      &35         & 1  & 1     & 0   & 3.4 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false detections.  Matches are determined using a
  3'' match radius with the input reference catalog.  Objects with the
  {\tt EDGE} flag are ignored.  We list the number of background
  fluctuations that are expected to randomly associate with a Source
  N$_{Random}$, given the density of objects in the images and a 3''
  match radius, assuming that N$_{Orphan}$ represents 96\% of the
  total population of detections arriving from Gaussian fluctuations.
  We also list the number of false detections that are found within
  the outer 100 pixels of the image N$_{D<100}$.  The final column
  lists ratios of the number of negatively detected false detections
  to those with positive flux, a 5--sigma. \label{tab-bestfp10}}
\end{table}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
\caption{``Heat--map'' detailing the total numbers of 5--sigma false
  positives as a function of two main degrees of freedom: the maximum
  order of basis Laguerre polynomials along the y--axis, and the
  spatial order of the Chebyshev expansion of the spatial model along
  the x--axis.  The {\it left} column shows these results for
  prefiltering, while the {\it right} column shows this for the
  post--filtered analysis.  The best results listed in
  Table~\ref{tab-bestfp10}, with the associated configurations from
  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
  subpanels.  }
\label{fp_heatmap}
\end{figure}
